---
title: "Accelerated Life Testing (ALT)"
output: 
  rmarkdown::html_vignette:
    fig_width: 7
    fig_height: 5
vignette: >
  %\VignetteIndexEntry{Accelerated Life Testing (ALT)}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(ReliaPlotR)
library(WeibullR)
library(WeibullR.ALT)
```

## Building an ALT Model

The `WeibullR.ALT` package uses a three-step pipeline to create an ALT model.

**Step 1 — Create data sets** for each stress level using `alt.data()`:

```{r data}
d1 <- alt.data(c(248, 456, 528, 731, 813, 537), stress = 300)
d2 <- alt.data(c(164, 176, 289), stress = 350)
d3 <- alt.data(c(88, 112, 152), stress = 400)
```

**Step 2 — Fit parallel models** across stress levels using `alt.make()` and `alt.parallel()`:

```{r parallel, results = "hide"}
obj <- alt.parallel(
  alt.make(list(d1, d2, d3), dist = "weibull", alt.model = "arrhenius", view_dist_fits = FALSE),
  view_parallel_fits = FALSE
)
```

**Step 3 — Fit the life-stress relationship** using `alt.fit()`:

```{r fit, results = "hide"}
obj <- alt.fit(obj)
```

## ALT Probability Plot

`plotly_alt()` overlays one probability-paper fit line per stress level. Data points show empirical plotting positions; lines show the theoretical Weibull (or lognormal) fit. Click a legend entry to toggle a stress level on or off.

```{r prob-plot}
plotly_alt(obj)
```

### Customization

The plot accepts several optional arguments:

```{r prob-custom}
plotly_alt(
  obj,
  main    = "Reliability Test Results",
  xlab    = "Hours to Failure",
  cols    = c("#1f77b4", "#ff7f0e", "#2ca02c"),
  showGrid = FALSE
)
```

## Life-Stress Relationship Plot

`plotly_rel()` displays how characteristic life (eta for Weibull, median life for lognormal) changes with stress level, along with the fitted Arrhenius or Power Law relationship.

```{r rel-plot}
plotly_rel(obj)
```

The plot includes:

- **Points** (×) — characteristic-life estimates from parallel fits at each stress level
- **Red line** — fitted life-stress relationship (Arrhenius or Power Law)
- **Dashed blue lines** — percentile bands (10th and 90th by default)

### Percentile Bands

Use the `percentiles` argument to change which percentile bands are shown:

```{r rel-percentiles}
plotly_rel(obj, percentiles = c(5, 50, 95))
```

### Hiding Percentile Lines

Set `showPerc = FALSE` to show only the fitted relationship line:

```{r rel-no-perc}
plotly_rel(obj, showPerc = FALSE)
```

### Customization

```{r rel-custom}
plotly_rel(
  obj,
  main    = "Arrhenius Life-Stress Relationship",
  fitCol  = "darkgreen",
  percCol = "steelblue",
  signif  = 4
)
```

## See Also

- [Life Data Analysis](weibull.html) — fit Weibull/lognormal models at a single stress level
- [Reliability Growth Analysis](rga.html) — track reliability improvement over time
- [Repairable Systems Analysis](repairable.html) — analyze recurrent events with MCF and NHPP models
