---
title: "MCP Tools"
output:
  rmarkdown::html_vignette:
    fig_width: 7
    fig_height: 5
bibliography: ../inst/REFERENCES.bib
vignette: >
  %\VignetteIndexEntry{MCP Tools}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
has_ellmer <- requireNamespace("ellmer", quietly = TRUE)
```

```{r setup}
library(ReliaPlotR)
```

## Overview

The [Model Context Protocol](https://modelcontextprotocol.io) (MCP) is an open standard that lets AI assistants call external tools as part of a conversation. `reliapltr_mcp_server()` launches a lightweight MCP server that exposes two reliability analysis tools to any MCP client, such as [Claude Code](https://claude.ai/code) or Claude Desktop:

| Tool | What it does |
|---|---|
| `fit_weibull` | Fit a Weibull or lognormal distribution to time-to-failure data and return parameter estimates |
| `fit_alt` | Fit an Accelerated Life Test (ALT) model across multiple stress levels and return life-stress relationship coefficients |

These tools complement the reliability growth tools (`rga`, `nhpp`, `duane`, `mcf`) already provided by the `ReliaGrowR` package's own MCP server.

## Installation

`mcptools` and `ellmer` are optional dependencies listed in `Suggests`. Install them before starting the server:

```{r install, eval = FALSE}
pak::pak(c("mcptools", "ellmer"))
```

## Registering with Claude Code

Once the packages are installed, register the server in your Claude Code session. Two equivalent approaches are available:

```{bash mcp-add-inline, eval = FALSE}
# Option 1: inline (works with any R installation)
claude mcp add -s user reliapltr -- \
  Rscript -e "ReliaPlotR::reliapltr_mcp_server()"
```

```{bash mcp-add-script, eval = FALSE}
# Option 2: bundled launcher script (after package installation)
claude mcp add -s user reliapltr -- \
  Rscript $(Rscript -e "cat(system.file('mcp/server.R', package='ReliaPlotR'))")
```

Confirm the server is registered:

```{bash mcp-list, eval = FALSE}
claude mcp list
```

Once registered, Claude Code will offer the `fit_weibull` and `fit_alt` tools automatically whenever it detects a reliability analysis task.

## The `fit_weibull` Tool

`fit_weibull` fits a Weibull or lognormal distribution to a vector of failure times, optionally with right-censored (suspension) data, and returns parameter estimates and a goodness-of-fit metric.

### Arguments

| Argument | Type | Default | Description |
|---|---|---|---|
| `failures` | numeric array | *required* | Failure times (positive numbers) |
| `suspensions` | numeric array | `NULL` | Right-censored times -- units still operating at end of test |
| `dist` | string | `"weibull"` | Distribution: `"weibull"`, `"lognormal"`, or `"weibull3p"` |
| `method_fit` | string | `"mle"` | Estimation method: `"mle"` (recommended for censored data) or `"rr-xony"` (rank regression) |
| `method_conf` | string | `"lrb"` | Confidence bounds: `"lrb"` (likelihood-ratio, requires MLE) or `"fm"` (Fisher-matrix). Automatically switches to `"fm"` when rank regression is used. |

### Example

The following shows what the tool returns when called from an MCP client. The same function can be invoked directly in R for testing:

```{r wblr-example, eval = has_ellmer}
# Five machines that failed at these times (hours)
tool <- ReliaPlotR:::.make_wblr_tool()
result <- tool(failures = c(30, 49, 82, 90, 96))
str(result)
```

The flat named list is serialized to JSON when returned over MCP. `param1` is the Weibull shape parameter $\beta$; `param2` is the characteristic life $\eta$.

Adding right-censored suspensions shifts the estimates to account for units that did not fail:

```{r wblr-susp, eval = has_ellmer}
result_susp <- tool(
  failures    = c(30, 49, 82, 90, 96),
  suspensions = c(100, 120, 150)
)
cat("Beta:", result_susp$param1, "\n")
cat("Eta: ", result_susp$param2, "\n")
```

## The `fit_alt` Tool

`fit_alt` runs the full ALT pipeline (`alt.make` → `alt.parallel` → `alt.fit`) across multiple stress levels and returns per-stress-level parameters alongside the fitted global life-stress relationship.

### Arguments

| Argument | Type | Default | Description |
|---|---|---|---|
| `stresses` | numeric array | *required* | One stress value per stress level, e.g. `[300, 350, 400]` |
| `failures_json` | string | *required* | JSON array of failure-time arrays, one inner array per stress level. Example: `'[[248,456,528],[164,176,289],[88,112,152]]'` |
| `dist` | string | `"weibull"` | Life distribution: `"weibull"` or `"lognormal"` |
| `alt_model` | string | `"arrhenius"` | Life-stress model: `"arrhenius"` (temperature) or `"power"` (non-thermal) |

### Example

```{r alt-example, eval = has_ellmer, results = "hide"}
tool_alt <- ReliaPlotR:::.make_alt_tool()
result_alt <- tool_alt(
  stresses      = c(300, 350, 400),
  failures_json = "[[248,456,528,731,813,537],[164,176,289],[88,112,152]]",
  dist          = "weibull",
  alt_model     = "arrhenius"
)
```

```{r alt-show, eval = has_ellmer}
# Per-stress-level parameter estimates
result_alt$parallel

# Global Arrhenius life-stress relationship coefficients
result_alt$relationship
```

The `P1` column in `$parallel` is the characteristic life $\eta$ at each stress level (for Weibull) or $\exp(\mu_{\log})$ (for lognormal). The `P2` column is the shape parameter $\beta$, constrained to be equal across stress levels. The `$relationship` coefficients `coef1` and `coef2` define the log-linear life-stress model [@Nelson1990].

## How the Tools Work

Each MCP tool wraps the same fitting pipeline used by the corresponding `plotly_*` function, then formats results using the `tidy_wblr()` and `tidy_alt()` accessor functions:

```
fit_weibull:   wblr() -> wblr.fit() -> wblr.conf() -> tidy_wblr() -> named list
fit_alt:    alt.make() -> alt.parallel() -> alt.fit() -> tidy_alt() -> named list
```

The accessor functions (`tidy_wblr()`, `tidy_alt()`, `tidy_rga()`) can also be called directly from R to extract parameter estimates from already-fitted model objects without going through MCP.

## References

## See Also

- [Life Data Analysis](weibull.html) -- fit Weibull/lognormal models interactively
- [Accelerated Life Testing](alt.html) -- full ALT workflow with probability and life-stress plots
- [Reliability Growth Analysis](rga.html) -- Crow-AMSAA and Duane models
- [Repairable Systems Analysis](repairable.html) -- MCF and NHPP models
