---
title: "Weibull Analysis"
output: 
  rmarkdown::html_vignette:
    fig_width: 7
    fig_height: 5
vignette: >
  %\VignetteIndexEntry{weibull}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

To run a Weibull Analysis, start by loading `WeibullR` and `ReliaPlotR`

```{r setup}
library(WeibullR)
library(ReliaPlotR)
```

## A Basic Example

Next, create some failure data for 5 different machines that fail at time 30, 49, 82, 90, and 96 respectively. 

```{r echo=TRUE}
failures <- c(30, 49, 82, 90, 96)
```

Then use the `WeibullR` package to fit a Weibull distribution to the data, and the `plotly_wblr()` function to create a probability plot.

```{r echo=TRUE}
obj <- wblr.conf(wblr.fit(wblr(failures)))
plotly_wblr(obj)
```

## Right Censored Model

Let's add right censored data to the previous example. In addition to the 5 machines that failed, add suspensions for 3 machines that did not fail (right censored) at times 100, 45, and 10 respectively.

```{r echo=TRUE}
suspensions <- c(100, 45, 10)
obj <- wblr.conf(wblr.fit(wblr(failures, suspensions)))
plotly_wblr(obj, suspensions, fitCol = "blue", confCol = "blue")
```

## Interval Censored Model

To create an interval censored model, let's use the inspection data from Silkworth, 2020.

```{r echo=TRUE}
inspection_data <- data.frame(
  left = c(0, 6.12, 19.92, 29.64, 35.4, 39.72, 45.32, 52.32),
  right = c(6.12, 19.92, 29.64, 35.4, 39.72, 45.32, 52.32, 63.48),
  qty = c(5, 16, 12, 18, 18, 2, 6, 17)
)
```

Then add suspension data for units surviving until the last inspection date.

```{r echo=TRUE}
suspensions <- data.frame(time = 63.48, event = 0, qty = 73)
```

Finally, add a fit and plot the results.

```{r echo=TRUE, warning=FALSE}
obj <- wblr(suspensions, interval = inspection_data)
obj <- wblr.fit(obj, method.fit = "mle")
obj <- wblr.conf(obj, method.conf = "fm", lty = 2)
suspensions <- as.vector(suspensions$time)
plotly_wblr(obj,
  susp = suspensions, fitCol = "red", confCol = "red", intCol = "blue",
  main = "Parts Cracking Inspection Interval Analysis",
  ylab = "Cumulative % Cracked", xlab = "Inspection Time"
)
```

## 3-Parameter Weibull Model

To fit a 3P Weibull, let's create some new failure data and plot the results.

```{r echo=TRUE}
failures <- c(25, 30, 42, 49, 55, 67, 73, 82, 90, 96, 101, 110, 120, 132, 145)
fit <- wblr.conf(wblr.fit(wblr(failures), dist = "weibull3p"))
plotly_wblr(fit, fitCol = "darkgreen", confCol = "darkgreen")
```

## Contour Plots

To build a contour plot, let's rerun the first example and use the `plotly_contour()` function to create a plot.

```{r echo=TRUE}
failures <- c(30, 49, 82, 90, 96)
obj <- wblr.conf(wblr.fit(wblr(failures), method.fit = "mle"), method.conf = "lrb")
plotly_contour(obj, col = "blue")
```
